---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# transrivalry

<!-- badges: start -->
<!-- badges: end -->

This package is used to analyze the transition data collected in the project of 
"Phenomenology of Transitions in Binocular Rivalry". These functions organizes
the data for the further statistical analysis. Moreover, one can visualize
the data and the descriptive statistics.

## Installation

You can install the released version of transrivalry from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("transrivalry")
```

## Preprocessing

We need to reorganize the data and combine all the data saved in separate files.

This is a basic example for preprocessing:

```{r example}
library(transrivalry)
datafold <- paste(getwd(), '/tests', sep='')
csv_path <- paste(datafold, '/data.csv',sep='')
subject_list <- c('s001','s003','s005','s006','s007')
basename <- 'assessments_'
data <- combine_all_subjects(csv_path,datafold,subject_list,basename,1)
```

## Descriptive statistics

To understand the nature of different transition types, we can check the 
parameters including frequency, duration and speed. Descriptive stats can give
a simple insight.

This is a basic example for statistics:
```{r example}
library(transrivalry)
datafold <- paste(getwd(), '/tests', sep='')
csv_path <- paste(datafold, '/data.csv',sep='')
subject_list <- c('s001','s003','s005','s006','s007')
basename <- 'assessments_'
data <- combine_all_subjects(csv_path,datafold,subject_list,basename,1)
data['category_code'] <- rep(c(1,1,1,2,2,2,3,3,4,5),79)
data <- normalize_data(data)
all_stats <- descriptive_transition(data)
```

## Visualization

This package can also visualize the descriptives of transition data. We can plot
each parameters separately across all transition types.

This is a basic example for visualization:
```{r example}
library(transrivalry)
datafold <- paste(getwd(), '/tests', sep='')
csv_path <- paste(datafold, '/data.csv',sep='')
subject_list <- c('s001','s003','s005','s006','s007')
basename <- 'assessments_'
data <- combine_all_subjects(csv_path,datafold,subject_list,basename,1)
data['category_code'] <- rep(c(1,1,1,2,2,2,3,3,4,5),79)
data <- normalize_data(data)
all_stats <- descriptive_transition(data)
plot_stats(all_stats,'median','frequency')
```
